Visualization of [fulle name] Fractional Integrals

### 2019-03-26 fractional/CMJ style files/article-template.tex
new sentences

The idea of integer-order differentiation and integration is well known to most undergraduates. However, undergraduates are less familiar with the idea of an arbitrary order differential or integral (i.e. fractional-order calculus).
Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. The reason fractional calsulus is not generally 
taught at the undegraduate level is partly due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. This paper 
is specifically written for undergraduate lecturers and is very pedigogical in nature. The aim of the paper is to motivate and enable undergraduate 
lectures to introduce undergraduate students to this fascinating mathematical discipline.

>>>>

The idea of integer-order differentiation and integration is well known to most undergraduates. However, undergraduates are less familiar with the idea of an arbitrary order differential or integral (i.e. fractional-order calculus).
Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. The reason fractional calsulus is not generally 
taught at the undegraduate level is partly due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. This paper 
is specifically written for undergraduate lecturers and is very pedigogical in nature. In this paper we present a novel geometric interpretation of the 
Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
